### 2020-03-11 README.Rmd
Leave readme like this, for now

pd <- paste0("%", -1*(max(nchar(levels(struc$file)))+2), "s")
out <- c("````", "```", ".", apply(struc, 1, function(thisrow){
  paste0("├── ", sprintf(pd, thisrow[1]), "<- ", thisrow[2])
}), "```", "````")
cat(out, sep = "\r\n")
```

>>>>

pd <- paste0("%", -1*(max(nchar(levels(struc$file)))+2), "s")
#out <- c("````", "```", ".", apply(struc, 1, function(thisrow){
#  paste0("├── ", sprintf(pd, thisrow[1]), "<- ", thisrow[2])
#}), "```", "````")
out <- c("```", ".", apply(struc, 1, function(thisrow){
  paste0("├── ", sprintf(pd, thisrow[1]), "<- ", thisrow[2])
}), "```")
cat(out, sep = "\r\n")
```
